Incentivizing Exploration with Unbiased Subhistories

### 2018-11-02 llevel-overview.tex
update

% In Theorem \ref{thm:llevel-2}, we show a policy with
Our second policy achieves an instance-dependent regret
guarantee. This policy has the same info-graph structure as the first
one in Theorem \ref{thm:llevel-1}, but requires a higher number of
levels $L = O(\log(T/\log\log(T)))$ and larger group sizes. We will
bound its regret as a function of the gap parameter $\Delta$ even
though the construction of the policy does not depend on $\Delta$. In
particular, this regret bound outperforms the one in Theorem
\ref{thm:llevel-1} when $\Delta$ is much bigger than $T^{-1/2}$.  It
also has the desirable property that the policy does not withhold too
much information from agents---any agent $t$ observes a good fraction
of history in previous rounds.

\begin{theorem}
\label{thm:llevel-2}
There exists a $O(\log(T)/\log\log(T))$-level policy such that for
every multi-armed bandit instance with gap parameter $\Delta$, the
policy has regret $$O_K(\min(1/\Delta, T^{1/2}) \cdot \polylog(T))$$
Moreover, under this policy, each agent $t$ observes a subhistory of
size at least $\Omega( t/\polylog(T))$.
\end{theorem}

Note for constant number of arms, this result mathches the optimal
regret rate (given in \Cref{eq:model-OptRegret}) for stochastic
bandits, up to logarithmic factors.

@@

A natural idea to extend the three-level policy is to insert more
levels as multiple ``check points", so the policy can incentivize the
agents to perform more adaptive exploration. However, we need to
introduce two main modifications in the info-graph two accomendate
some new challenges. We will first informally describe our techniques
for the two-arm case.

@@

\paragraph{Amplifying groups for boundary cases.} Recall in the
three-level policy, the medium gap case (Lemma \ref{3levelmedium})
corresponds to the case where the gap $\Delta$ is between
$\Omega\left(\sqrt{{1}/({\log(T) T_1)}}\right)$ and
$O\left(\sqrt{{1}/{T_1}}\right)$. This is a boundary case since
$\Delta$ is neither large enough to conclude that with high
probability agents in both the second level and the third level all
pull the best arm, nor small enough to conclude that both arms are
explored enough times in the second level (due to
anti-concentration). In this case, we need to ensure that agents in
the third level can eliminate the inferior arm. This issue is easily
resolved in the three-level policy since the agents in the third level
observe the entire first-level history, which consists of
$\Omega(\log(T) T_1)$ pulls of each arm and provides sufficiently
accurate reward estimates to distinguish the two arms.

@@

In the $L$-level policy, such boundary cases occur for each
intermediate level $l\in \{2, \ldots, l-1\}$, but the issue mentioned
above does not get naturally resolved since the ratios between the
upper and lower bounds of $\Delta$ rise from $\Theta(\sqrt{\log(T)})$
to $\Theta(\log(T))$, and it would require more observations from
level $(l-2)$ to distinguish two arms at level $l$. The reason for
this larger disparity is that, except the first level, we can no
longer guarantee sufficient number of pulls of each arm. For example,
as shown in Figure \ref{fig:llevel-connecting}, when we talk about
having enough arm $a$ pulls in the history observed by agents in
$G_{l,1,1}$, it could be that only agents in group $G_{l-1,1,1}$ are
pulling arm $a$ and it also could be that most agents in groups
$G_{l-1,1,1},G_{l-1,1,2},...,G_{l-1,1,\NG}$ are pulling arm
$a$. Therefore our estimate of the number of arm $a$ pulls can be off
by an $\NG=\Theta(\log(T))$ multiplicative factor. This ultimately
makes the boundary cases harder to deal with.

We resolve this problem by introducing an additional type of \emph{amplifying groups}, called $\Gamma$-groups. For each $l \in [L], u,v \in [\NG]$, we create a $\Gamma$-group $\Gamma_{l,u,v}$. Agents in $\Gamma_{l,u,v}$ observe the same history as the one observed by agents in $G_{l,u,v}$ and the number of agents in $\Gamma_{l,u,v}$ is $\Theta(\log(T)$ times the number of agents in $G_{l,u,v}$. The main difference between the $G$-groups and $\Gamma$-groups is that the history of $\Gamma$-groups in level $l$ is not sent to agents in level $l+1$ but agents in higher levels. When we are in the boundary case in which we don't have good guarantees about the $l+1$ level agents' pulls, the new construction makes sure that agents in levels higher than $l+1$ get enough pulls of each arm and all pull the best arm. 
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:

>>>>

% In Theorem \ref{thm:llevel-2}, we show a policy with
Our second policy achieves an instance-dependent regret
guarantee. This policy has the same info-graph structure as the first
one in Theorem \ref{thm:llevel-1}, but requires a higher number of
levels $L = O(\log(T/\log\log(T)))$ and different group sizes. We will
bound its regret as a function of the gap parameter $\Delta$ even
though the construction of the policy does not depend on $\Delta$. In
particular, this regret bound outperforms the one in Theorem
\ref{thm:llevel-1} when $\Delta$ is much bigger than $T^{-1/2}$.  It
also has the desirable property that the policy does not withhold too
much information from agents---any agent $t$ observes a good fraction
of history in previous rounds.

\begin{theorem}
\label{thm:llevel-2}
There exists an $O(\log(T)/\log\log(T))$-level policy such that for
every multi-armed bandit instance with gap parameter $\Delta$, the
policy has regret $$O_K(\min(1/\Delta, T^{1/2}) \cdot \polylog(T))$$
Moreover, under this policy, each agent $t$ observes a subhistory of
size at least $\Omega( t/\polylog(T))$.
\end{theorem}

Note for constant number of arms, this result matches the optimal
regret rate (given in \Cref{eq:model-OptRegret}) for stochastic
bandits, up to logarithmic factors.

@@

A natural idea to extend the three-level policy is to insert more
levels as multiple ``check points", so the policy can incentivize the
agents to perform more adaptive exploration. However, we need to
introduce two main modifications in the info-graph to accommodate
some new challenges. We will first informally describe our techniques
for the two-arm case.

@@

\paragraph{Amplifying groups for boundary cases.} Recall in the
three-level policy, the medium gap case (Lemma \ref{3levelmedium})
corresponds to the case where the gap $\Delta$ is between
$\Omega\left(\sqrt{{1}/({T_1})}\right)$ and
$O\left(\sqrt{{\log(T)}/{T_1}}\right)$. This is a boundary case since
$\Delta$ is neither large enough to conclude that with high
probability agents in both the second level and the third level all
pull the best arm, nor small enough to conclude that both arms are
explored enough times in the second level (due to
anti-concentration). In this case, we need to ensure that agents in
the third level can eliminate the inferior arm. This issue is easily
resolved in the three-level policy since the agents in the third level
observe the entire first-level history, which consists of
$\Omega(T_1\log(T))$ pulls of each arm and provides sufficiently
accurate reward estimates to distinguish the two arms.

@@

In the $L$-level policy, such boundary cases occur for each
intermediate level $l\in \{2, \ldots, l-1\}$, but the issue mentioned
above does not get naturally resolved since the ratios between the
upper and lower bounds of $\Delta$ rise from $\Theta(\sqrt{\log(T)})$
to $\Theta(\log(T))$, and it would require more observations from
level $(l-2)$ to distinguish two arms at level $l$. The reason for
this larger disparity is that, except the first level, our guarantee on 
the number of pulls of each arm is no longer tight. For example,
as shown in Figure \ref{fig:llevel-connecting}, when we talk about
having enough arm $a$ pulls in the history observed by agents in
$G_{l,1,1}$, it could be that only agents in group $G_{l-1,1,1}$ are
pulling arm $a$ and it also could be that most agents in groups
$G_{l-1,1,1},G_{l-1,1,2},...,G_{l-1,1,\NG}$ are pulling arm
$a$. Therefore our estimate of the number of arm $a$ pulls can be off
by an $\NG=\Theta(\log(T))$ multiplicative factor. This ultimately
makes the boundary cases harder to deal with.

We resolve this problem by introducing an additional type of \emph{amplifying groups}, called $\Gamma$-groups. For each $l \in [L], u,v \in [\NG]$, we create a $\Gamma$-group $\Gamma_{l,u,v}$. Agents in $\Gamma_{l,u,v}$ observe the same history as the one observed by agents in $G_{l,u,v}$ and the number of agents in $\Gamma_{l,u,v}$ is $\Theta(\log(T))$ times the number of agents in $G_{l,u,v}$. The main difference between $G$-groups and $\Gamma$-groups is that the history of $\Gamma$-groups in level $l$ is not sent to agents in level $l+1$ but agents in higher levels. When we are in the boundary case in which we don't have good guarantees about the $l+1$ level agents' pulls, the new construction makes sure that agents in levels higher than $l+1$ get to see enough pulls of each arm and all pull the best arm. 
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:
